Estimating the number of clusters using Cross Validation

### 2015-06-08 cvclust.tex
Describe simulation, add figure

We confirm this with a simulation.  [TODO: add simulation]

>>>>

We confirm this with a simulation.  We perform $10$ replicates.  In each
replicate, we generate $20000$ observations from a mean-zero bivariate normal
distribution with unit marginal variances and correlation $\rho$.  We perform
a single $2 \times 2$ fold of Gabriel cross-validation and report the
cross-validation mean squared error for the number of clusters $k$ ranging
from $1$ to $5$.  Figure~\ref{fig:null-2d-corr-equal} shows the
cross-validation errors for all $10$ replicates.  The simulation demonstrates
that in the Gabriel cross-validation criterion chooses the correct answer $k =
1$ whenever $\rho < 0.5$; the criterion chooses $k = 2$ clusters whenever
$|\rho| > 0.5$.

\begin{figure}
\centering
\includegraphics[width=25pc]{figure/null-2d-corr-equal.pdf}
\caption{Cross-validation error on $10$ replicates, with the number of
clusters $k$ ranging from $1$ to $5$.  Data is generated from two-dimensional
multivariate normal distribution with correlation $\rho$.  The Gabriel
cross-validation criterion chooses the correct answer $k = 1$ whenever
$\rho < 0.5$; the criterion chooses $k = 2$ clusters whenever $|\rho| > 0.5$.}
\label{fig:null-2d-corr-equal}
\end{figure}
